---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Installing {ssd4mosaic}

You can install the stable version of `{ssd4mosaic}` from CRAN:

``` {r}
install.packages("ssd4mosaic")
```


The development version of `{ssd4mosaic}` can be installed from GitHub using the
`{remotes}` package: 

```{r}
remotes::install_gitlab("mosaic-software/mosaic-ssd@master",
                        host = "gitlab.in2p3.fr",
                        build_vignettes = TRUE)
```

## Launching the web application

The web application can be launched locally using the `run_app()` function. This
will launch the same application as what can be seen on the
[MOSAIC website](https://mosaic.univ-lyon1.fr/ssd).

```{r setup}
library(ssd4mosaic)
run_app()
```

A user guide is available directly in the application for further instructions.

If you are interested in using the functionalities of the SSD web application
directly in R, you may want to check the dedicated vignette, "Using ssd4mosaic's
functions in R".
